---
title: 'Targeted Indoor Residual Spraying (TIRS) Effectiveness in Mérida, 2023'
author: "Yining(Carina) Fu"
output: 
    flexdashboard::flex_dashboard:
      orientation: columns
      vertical_layout: fill
      navbar:
        - { title: "GitHub", href: "https://github.com/yiningfu619/tirsAnalysis", align: right, icon: "fa-github" }
        - { title: "Source Code", href: "https://github.com/yiningfu619/tirsAnalysis/blob/main/index.Rmd", align: right, icon: "fa-code" }
theme: cosmo
---

```{r setup, include=FALSE}
# ==========================================
# Load required packages (shiny removed)
# ==========================================
library(flexdashboard)
library(htmltools)
library(dplyr)
library(ggplot2)
library(lubridate)
library(tidyr)
library(scales)
library(plotly)
library(DT)

tnd.tirs <- read.csv("/Users/fuyi/Library/CloudStorage/OneDrive-Emory/DATA555/tnd_tirs_data.csv")
```

```{css}
.chart-stage,
.section.level3,
.sidebar {
  overflow: visible !important;
}

.chart-wrapper {
  border-radius: 10px;
  border: 1px solid #d9d9d9;
  box-shadow: 0 1px 2px rgba(0,0,0,0.04);
  background: #ffffff;
}

.chart-title {
  font-weight: 700;
  color: #1f3b73;
}

.small-note {
  color: #6b7280;
  font-size: 15px;
  margin-top: -6px;
  margin-bottom: 12px;
}

/* ===== Tau card ===== */
.tau-card-final {
  background: linear-gradient(180deg, #ef5350 0%, #e53935 100%);
  color: white;
  border-radius: 10px;
  padding: 16px 18px 14px 18px;
  min-height: 120px;
  box-shadow: 0 2px 6px rgba(0,0,0,0.08);
  margin-top: 0;
  text-align: center;
}

.tau-main-line {
  font-size: 34px;
  font-weight: 800;
  line-height: 1.1;
  margin-bottom: 10px;
}

.tau-mid-line {
  font-size: 20px;
  font-weight: 700;
  line-height: 1.2;
  margin-bottom: 10px;
}

.tau-bottom-line {
  font-size: 14px;
  font-weight: 600;
  line-height: 1.2;
  opacity: 0.98;
}

/* hide tau panel title, but keep the panel itself */
.tau-panel .chart-title {
  display: none !important;
}

/* give tau panel a little breathing room without pushing upward */
.tau-panel .chart-stage {
  padding-top: 14px !important;
  padding-bottom: 6px !important;
}

/* stop weird collapsing behavior */
.tau-panel .chart-wrapper {
  min-height: auto !important;
}

/* ===== Interpretation card ===== */
.interp-card {
  background: #eaf3fb;
  border-radius: 10px;
  padding: 18px;
  min-height: 190px;
  border: 1px solid #d9e7f6;
}

/* ===== Footer note ===== */
.results-note {
  color: #6b7280;
  font-size: 15px;
  margin-top: 6px;
}

table {
  font-size: 15px;
}
```

```{r data-clean, include=FALSE}
# ==========================================
# Data cleaning, extract Year column explicitly
# ==========================================
clean_df <- tnd.tirs %>%
  mutate(
    var6_pcr_date = as.character(var6_pcr_date),
    var6_pcr_date = na_if(var6_pcr_date, ""),
    Date = suppressWarnings(mdy(var6_pcr_date)),
    Year = year(Date)
  ) 

# ==========================================
# Generate base summary data (keep all 0s, handle Year labels)
# ==========================================
summary_base <- clean_df %>%
  group_by(Year) %>%
  summarise(
    DENV = sum(var6_pcr_res___1 == "Checked", na.rm = TRUE),
    ZIKV = sum(var6_pcr_res___2 == "Checked", na.rm = TRUE),
    CHIKV = sum(var6_pcr_res___3 == "Checked", na.rm = TRUE),
    .groups = "drop" 
  ) %>%
  mutate(Year = ifelse(is.na(Year), "Unknown", as.character(Year)))

# ==========================================
# Prepare data for [Bar Chart]
# ==========================================
summary_data_bar <- summary_base %>%
  pivot_longer(cols = c(DENV, ZIKV, CHIKV), names_to = "Virus", values_to = "Count") %>%
  filter(Count > 0) %>% 
  group_by(Year) %>%
  mutate(
    Prop = Count / sum(Count),
    Label = paste0(Virus, "\n", Count, "\n(", percent(Prop, accuracy = 0.1), ")")
  ) %>%
  ungroup()
```

Background {data-icon="fa-chalkboard"}
=======================================================================

Column {.sidebar data-width=200}
-----------------------------------------------------------------------

### 📌 Data Note
> All tables and figures presented on this page are derived from the test-negative design (TND) subset, representing a specific analytical cohort rather than the raw overall population.

Column {data-width="500"}
---------------------------------

### Data Summary Table

```{r}
# ==========================================
# Prepare and generate data for [Table] (including Total)
# ==========================================
table_data <- summary_base %>%
  mutate(Total = DENV + ZIKV + CHIKV) %>%
  bind_rows(
    summarise(., 
      Year = "Total",
      DENV = sum(DENV, na.rm = TRUE),
      ZIKV = sum(ZIKV, na.rm = TRUE),
      CHIKV = sum(CHIKV, na.rm = TRUE),
      Total = sum(Total, na.rm = TRUE)
    )
  )

knitr::kable(table_data, align = "c")
```


### 2023 DENV-3 Summary

```{r}
# ---------------------------------------------------------
# Prepare 2023 DENV-3 Season Data (Jul-Dec, exact months)
# ---------------------------------------------------------
df_denv3_bg <- tnd.tirs %>% 
  mutate(participant_id = paste0(record_id, "_", rn2_pt_id)) %>%
  dplyr::select(participant_id, cl_nr, rn1_br, var6_symp_date, var6_abv_pos___1, var6_denv_type___3) %>%
  mutate(
    cluster = as.character(cl_nr),
    illness_onset = as.Date(var6_symp_date, format = "%m/%d/%Y"),
    intervention = factor(rn1_br, levels = c(1, 2), labels = c("Control", "TIRS")),
    is_case = as.numeric(var6_abv_pos___1),
    is_denv3 = case_when(
      as.character(var6_denv_type___3) %in% c("Checked", "1") ~ 1,
      is_case == 0 ~ 0,
      TRUE ~ NA_real_
    )
  ) %>%
  filter(illness_onset >= as.Date("2023-07-01") & illness_onset <= as.Date("2023-12-31")) %>%
  drop_na(illness_onset, cluster, intervention, is_denv3) %>%
  distinct(participant_id, illness_onset, .keep_all = TRUE)
```

```{r}
plot_data <- df_denv3_bg %>%
  filter(is_denv3 == 1)

weekly_counts <- plot_data %>%
  mutate(Week = floor_date(illness_onset, unit = "week", week_start = 1)) %>%
  count(Week, name = "Weekly_Cases") %>%
  tidyr::complete(
    Week = seq(
      floor_date(as.Date("2023-07-01"), unit = "week", week_start = 1),
      floor_date(as.Date("2023-12-31"), unit = "week", week_start = 1),
      by = "1 week"
    ),
    fill = list(Weekly_Cases = 0)
  ) %>%
  mutate(
    Week_End = Week + 6,
    hover_text = paste0(
      "Week: ", format(Week, "%b %d"), " - ", format(Week_End, "%b %d, %Y"), "\n",
      "Cases: ", Weekly_Cases
    )
  )

p_weekly_smooth <- ggplot() +
  geom_col(
    data = weekly_counts,
    aes(x = Week, y = Weekly_Cases, text = hover_text),
    fill = "#56B4E9", width = 6, color = "white", alpha = 0.8
  ) +
  geom_smooth(
    data = weekly_counts,
    aes(x = Week, y = Weekly_Cases),
    method = "loess", span = 0.35, se = FALSE,
    color = "#E69F00", linewidth = 1.2
  ) +
  scale_x_date(
    limits = c(as.Date("2023-06-26"), as.Date("2024-01-07")),
    breaks = seq(as.Date("2023-07-03"), as.Date("2023-12-25"), by = "2 weeks"),
    date_labels = "%b %d"
  ) +
  theme_minimal() +
  labs(
    x = "Week of Illness Onset",
    y = "Number of DENV-3 Cases",
    title = "DENV-3 Weekly Case Distribution (Jul-Dec 2023)"
  ) +
  theme(
    axis.text.x = element_text(size = 10, angle = 45, hjust = 1),
    axis.text.y = element_text(size = 11),
    panel.grid.minor = element_blank()
  )

ggplotly(p_weekly_smooth, tooltip = "text")
```

> The monthly distribution reveals a sharp peak in DENV-3 cases during August 2023, reaching 15 cases. Following this sudden spike, the case count rapidly declined, with zero new cases reported from September 2023 through January 2024.


Column {data-width="500"}
---------------------------------

### Age of Participants in Each Block

```{r}
df_unique <- clean_df %>%
  distinct(record_id, .keep_all = TRUE)

df_unique <- df_unique %>%
  mutate(
    age = as.numeric(Age),
    Block_Type = factor(Block.Type)
  ) %>%
  group_by(Block_Type) %>%
  mutate(Block_Label = paste0(Block_Type, "\n(n=", n(), ")")) %>%
  ungroup()

p <- ggplot(df_unique, aes(
  x = Block_Label,
  y = Age,
  fill = Block_Type,
  text = paste("ID:", record_id, "<br>Age:", age)
)) +
  geom_boxplot(outlier.alpha = 0.3) +
  geom_jitter(width = 0.15, alpha = 0.3, size = 1) +
  theme_minimal() +
  labs(x = "Block Type", y = "Age", fill = "Block Type")

ggplotly(p, tooltip = "text")
```

> The boxplots indicate that participant age distributions are highly comparable between the Central and Periphery blocks, with both exhibiting a median age around 10 years. Additionally, the plot shows that the External block contains only a single data point (n=1), which prevents a meaningful comparison of its distribution.


TAU {data-icon="fa-chart-simple"}
=======================================================================

```{r tau-prep, include=FALSE}
# ---------------------------
# DENV-3 DATA
# ---------------------------
df_denv3_season <- tnd.tirs %>%
  mutate(participant_id = paste0(record_id, "_", rn2_pt_id)) %>%
  mutate(
    cluster = as.character(cl_nr),
    illness_onset = as.Date(var6_symp_date, format = "%m/%d/%Y"),
    intervention = factor(rn1_br, levels = c(1,2), labels = c("Control","TIRS")),
    is_case = as.numeric(var6_abv_pos___1),
    is_denv3 = case_when(
      as.character(var6_denv_type___3) %in% c("Checked","1") ~ 1,
      is_case == 0 ~ 0,
      TRUE ~ NA_real_
    ),
    Season_Part = case_when(
      illness_onset >= as.Date("2023-07-01") & illness_onset < as.Date("2023-09-01") ~ "1. Early (Jul-Aug)",
      illness_onset >= as.Date("2023-09-01") & illness_onset < as.Date("2023-11-01") ~ "2. Mid (Sep-Oct)",
      illness_onset >= as.Date("2023-11-01") & illness_onset <= as.Date("2023-12-31") ~ "3. Late (Nov-Dec)",
      TRUE ~ NA_character_
    )
  ) %>%
  filter(!is.na(Season_Part)) %>%
  drop_na(illness_onset, cluster, intervention, is_denv3) %>%
  distinct(participant_id, illness_onset, .keep_all = TRUE)

# ---------------------------
# ABV DATA
# ---------------------------
df_tau_ready <- tnd.tirs %>%
  mutate(participant_id = paste0(record_id, "_", rn2_pt_id)) %>%
  mutate(
    cluster = as.character(cl_nr),
    illness_onset = as.Date(var6_symp_date, format = "%m/%d/%Y"),
    intervention = factor(rn1_br, levels = c(1,2), labels = c("Control","TIRS")),
    is_case = as.numeric(var6_abv_pos___1),
    Season_Part = case_when(
      illness_onset >= as.Date("2023-07-01") & illness_onset < as.Date("2023-09-01") ~ "1. Early (Jul-Aug)",
      illness_onset >= as.Date("2023-09-01") & illness_onset < as.Date("2023-11-01") ~ "2. Mid (Sep-Oct)",
      illness_onset >= as.Date("2023-11-01") & illness_onset <= as.Date("2023-12-31") ~ "3. Late (Nov-Dec)",
      TRUE ~ NA_character_
    )
  ) %>%
  drop_na(illness_onset, cluster, is_case, intervention, Season_Part) %>%
  distinct(participant_id, illness_onset, .keep_all = TRUE)

# ---------------------------
# DENV-3 tau function
# ---------------------------
calculate_denv3_tau <- function(df, t_window = 30) {
  n <- nrow(df)
  if (n < 2) {
    return(data.frame(
      `Neighborhood Pairs (Both Positive)` = NA,
      `Neighborhood Pairs (At least 1 Negative)` = NA,
      `Neighborhood Odds` = NA,
      `Citywide Pairs (Both Positive)` = NA,
      `Citywide Pairs (At least 1 Negative)` = NA,
      `Citywide Odds` = NA,
      `Clustering Ratio (Tau)` = NA,
      check.names = FALSE
    ))
  }
  time_mat   <- abs(outer(as.numeric(df$illness_onset), as.numeric(df$illness_onset), "-")) <= t_window
  cluster_mat <- outer(df$cluster, df$cluster, "==")
  linked_mat  <- outer(df$is_denv3 == 1, df$is_denv3 == 1, "&")
  person_mat  <- outer(df$participant_id, df$participant_id, "==")
  time_valid  <- time_mat & upper.tri(time_mat) & !person_mat
  local_pairs_mask  <- time_valid & cluster_mat
  a_local  <- sum(local_pairs_mask & linked_mat)
  b_local  <- sum(local_pairs_mask & !linked_mat)
  theta_cluster   <- ifelse(b_local == 0, NA, a_local / b_local)
  global_pairs_mask <- time_valid
  a_global  <- sum(global_pairs_mask & linked_mat)
  b_global  <- sum(global_pairs_mask & !linked_mat)
  theta_anywhere  <- ifelse(b_global == 0, NA, a_global / b_global)
  tau <- ifelse(
    is.na(theta_cluster) | is.na(theta_anywhere) | theta_anywhere == 0,
    NA, theta_cluster / theta_anywhere
  )
  data.frame(
    `Neighborhood Pairs (Both Positive)` = a_local,
    `Neighborhood Pairs (At least 1 Negative)` = b_local,
    `Neighborhood Odds` = theta_cluster,
    `Citywide Pairs (Both Positive)` = a_global,
    `Citywide Pairs (At least 1 Negative)` = b_global,
    `Citywide Odds` = theta_anywhere,
    `Clustering Ratio (Tau)` = tau,
    check.names = FALSE
  )
}

# ---------------------------
# ABV tau function
# ---------------------------
calculate_new_tau <- function(df, t_window = 30) {
  if (nrow(df) < 2) {
    return(data.frame(
      `Neighborhood Pairs (Both Positive)` = NA,
      `Neighborhood Pairs (At least 1 Negative)` = NA,
      `Neighborhood Odds` = NA,
      `Citywide Pairs (Both Positive)` = NA,
      `Citywide Pairs (At least 1 Negative)` = NA,
      `Citywide Odds` = NA,
      `Clustering Ratio (Tau)` = NA,
      check.names = FALSE
    ))
  }
  time_mat    <- abs(outer(as.numeric(df$illness_onset), as.numeric(df$illness_onset), "-")) <= t_window
  cluster_mat <- outer(df$cluster, df$cluster, "==")
  linked_mat  <- outer(df$is_case == 1, df$is_case == 1, "&")
  person_mat  <- outer(df$participant_id, df$participant_id, "==")
  time_valid  <- time_mat & upper.tri(time_mat) & !person_mat
  local_pairs_mask  <- time_valid & cluster_mat
  a_local  <- sum(local_pairs_mask & linked_mat)
  b_local  <- sum(local_pairs_mask & !linked_mat)
  theta_cluster   <- ifelse(b_local == 0, NA, a_local / b_local)
  global_pairs_mask <- time_valid
  a_global  <- sum(global_pairs_mask & linked_mat)
  b_global  <- sum(global_pairs_mask & !linked_mat)
  theta_anywhere  <- ifelse(b_global == 0, NA, a_global / b_global)
  tau <- ifelse(
    is.na(theta_cluster) | is.na(theta_anywhere) | theta_anywhere == 0,
    NA, theta_cluster / theta_anywhere
  )
  data.frame(
    `Neighborhood Pairs (Both Positive)` = a_local,
    `Neighborhood Pairs (At least 1 Negative)` = b_local,
    `Neighborhood Odds` = theta_cluster,
    `Citywide Pairs (Both Positive)` = a_global,
    `Citywide Pairs (At least 1 Negative)` = b_global,
    `Citywide Odds` = theta_anywhere,
    `Clustering Ratio (Tau)` = tau,
    check.names = FALSE
  )
}

# ---------------------------
# Pre-compute all combinations
# ---------------------------
season_levels <- c("1. Early (Jul-Aug)", "2. Mid (Sep-Oct)", "3. Late (Nov-Dec)")
windows       <- seq(7, 60, by = 7)
default_window <- 30

combos <- expand.grid(
  disease = c("DENV-3", "ABV"),
  season  = season_levels,
  stringsAsFactors = FALSE
)

# Results at default window (for odds charts and tau summary table)
odds_data <- lapply(seq_len(nrow(combos)), function(i) {
  d <- combos$disease[i]; s <- combos$season[i]
  df  <- if (d == "DENV-3") df_denv3_season %>% filter(Season_Part == s) else df_tau_ready %>% filter(Season_Part == s)
  res <- if (d == "DENV-3") calculate_denv3_tau(df, default_window) else calculate_new_tau(df, default_window)
  list(
    local_linked    = res$`Neighborhood Pairs (Both Positive)`[[1]],
    local_unlinked  = res$`Neighborhood Pairs (At least 1 Negative)`[[1]],
    global_linked   = res$`Citywide Pairs (Both Positive)`[[1]],
    global_unlinked = res$`Citywide Pairs (At least 1 Negative)`[[1]],
    local_odds      = res$`Neighborhood Odds`[[1]],
    global_odds     = res$`Citywide Odds`[[1]],
    tau             = res$`Clustering Ratio (Tau)`[[1]]
  )
})
names(odds_data) <- paste(combos$disease, combos$season, sep = "|")

# Tau values across all windows (for tau vs time window chart)
tau_all <- lapply(seq_len(nrow(combos)), function(i) {
  d <- combos$disease[i]; s <- combos$season[i]
  sapply(windows, function(w) {
    df  <- if (d == "DENV-3") df_denv3_season %>% filter(Season_Part == s) else df_tau_ready %>% filter(Season_Part == s)
    res <- if (d == "DENV-3") calculate_denv3_tau(df, w) else calculate_new_tau(df, w)
    res$`Clustering Ratio (Tau)`[[1]]
  })
})
names(tau_all) <- paste(combos$disease, combos$season, sep = "|")

# Default combo index (DENV-3, Mid season)
default_idx <- which(combos$disease == "DENV-3" & combos$season == "2. Mid (Sep-Oct)")
```

Column {data-width=280}
-----------------------------------------------------------------------

### Controls

```{r}
HTML("
<div style='font-size:14px; color:#374151; line-height:1.8; padding:4px 2px;'>
  <p>Use the <b>dropdown menus</b> embedded in each chart to switch between outcomes and season phases.</p>
  <hr style='margin:8px 0; border-color:#e5e7eb;'>
  <p><b>Outcome:</b> DENV-3 or Aedes-borne diseases (ABV)</p>
  <p><b>Season phase:</b><br>
    &nbsp;• Early (Jul–Aug)<br>
    &nbsp;• Mid (Sep–Oct)<br>
    &nbsp;• Late (Nov–Dec)
  </p>
  <p><b>Time window:</b> Odds charts are fixed at <b>30 days</b>. The τ vs Time Window chart shows all windows (7–60 days).</p>
</div>
")
```

### τ Summary (Window = 30 days)

```{r}
tau_summary_df <- data.frame(
  Disease = combos$disease,
  Season  = gsub("^\\d+\\. ", "", combos$season),
  `τ`     = sapply(odds_data, function(x) ifelse(is.na(x$tau), "—", sprintf("%.3f", x$tau))),
  Result  = sapply(odds_data, function(x) {
    if (is.na(x$tau))    "Insufficient pairs"
    else if (x$tau > 1)  "Clustering detected"
    else if (x$tau == 1) "No difference"
    else                 "Weak clustering"
  }),
  check.names = FALSE
)

DT::datatable(
  tau_summary_df,
  options = list(pageLength = 6, dom = "t", ordering = FALSE),
  rownames = FALSE
) %>%
  DT::formatStyle(
    "Result",
    backgroundColor = DT::styleEqual(
      c("Clustering detected", "Weak clustering", "Insufficient pairs"),
      c("#d1fae5", "#fef3c7", "#f3f4f6")
    )
  )
```

Column {data-width=500}
-----------------------------------------------------------------------

### Local Odds (Within Cluster)

Pairs of individuals in the **same cluster** within the time window (30 days). Use the dropdown to switch outcome / season.

```{r}
p_local <- plot_ly()

for (i in seq_len(nrow(combos))) {
  d   <- combos$disease[i]; s <- combos$season[i]
  key <- paste(d, s, sep = "|")
  od  <- odds_data[[key]]
  vis <- (i == default_idx)
  counts <- c(od$local_linked, od$local_unlinked)
  counts[is.na(counts)] <- 0

  p_local <- add_trace(
    p_local,
    x    = c("Linked", "Unlinked"),
    y    = counts,
    type = "bar",
    name = paste(d, gsub("^\\d+\\. ", "", s), sep = " | "),
    visible    = vis,
    showlegend = FALSE,
    marker     = list(color = c("#2f69b1", "#a9c2df")),
    text       = paste0(c("Linked", "Unlinked"), ": ", comma(counts)),
    hoverinfo  = "text"
  )
}

make_local_annotation <- function(i) {
  lo  <- odds_data[[paste(combos$disease[i], combos$season[i], sep = "|")]]$local_odds
  txt <- if (is.na(lo)) "Neighborhood Odds = NA" else paste0("<b>Neighborhood Odds = ", sprintf("%.2f", lo), "</b>")
  list(list(x = 0.5, y = -0.22, xref = "paper", yref = "paper",
            text = txt, showarrow = FALSE, font = list(size = 13)))
}

buttons_local <- lapply(seq_len(nrow(combos)), function(i) {
  vis <- rep(FALSE, nrow(combos)); vis[i] <- TRUE
  list(
    method = "update",
    args   = list(list(visible = as.list(vis)),
                  list(annotations = make_local_annotation(i))),
    label  = paste(combos$disease[i], gsub("^\\d+\\. ", "", combos$season[i]), sep = " | ")
  )
})

p_local %>%
  layout(
    updatemenus = list(list(
      type = "dropdown", x = 0.0, y = 1.20, xanchor = "left",
      buttons = buttons_local, active = default_idx - 1
    )),
    xaxis       = list(title = ""),
    yaxis       = list(title = "Pair Count"),
    showlegend  = FALSE,
    height      = 270,
    margin      = list(t = 55, b = 60),
    annotations = make_local_annotation(default_idx)
  ) %>%
  config(displayModeBar = FALSE)
```

### Baseline Odds (Anywhere)

Pairs of individuals **anywhere in the city** within the time window (30 days). Use the dropdown to switch outcome / season.

```{r}
p_global <- plot_ly()

for (i in seq_len(nrow(combos))) {
  d   <- combos$disease[i]; s <- combos$season[i]
  key <- paste(d, s, sep = "|")
  od  <- odds_data[[key]]
  vis <- (i == default_idx)
  counts <- c(od$global_linked, od$global_unlinked)
  counts[is.na(counts)] <- 0

  p_global <- add_trace(
    p_global,
    x    = c("Linked", "Unlinked"),
    y    = counts,
    type = "bar",
    name = paste(d, gsub("^\\d+\\. ", "", s), sep = " | "),
    visible    = vis,
    showlegend = FALSE,
    marker     = list(color = c("#58b947", "#b7d9ad")),
    text       = paste0(c("Linked", "Unlinked"), ": ", comma(counts)),
    hoverinfo  = "text"
  )
}

make_global_annotation <- function(i) {
  go  <- odds_data[[paste(combos$disease[i], combos$season[i], sep = "|")]]$global_odds
  txt <- if (is.na(go)) "Citywide Odds = NA" else paste0("<b>Citywide Odds = ", sprintf("%.2f", go), "</b>")
  list(list(x = 0.5, y = -0.22, xref = "paper", yref = "paper",
            text = txt, showarrow = FALSE, font = list(size = 13)))
}

buttons_global <- lapply(seq_len(nrow(combos)), function(i) {
  vis <- rep(FALSE, nrow(combos)); vis[i] <- TRUE
  list(
    method = "update",
    args   = list(list(visible = as.list(vis)),
                  list(annotations = make_global_annotation(i))),
    label  = paste(combos$disease[i], gsub("^\\d+\\. ", "", combos$season[i]), sep = " | ")
  )
})

p_global %>%
  layout(
    updatemenus = list(list(
      type = "dropdown", x = 0.0, y = 1.20, xanchor = "left",
      buttons = buttons_global, active = default_idx - 1
    )),
    xaxis       = list(title = ""),
    yaxis       = list(title = "Pair Count"),
    showlegend  = FALSE,
    height      = 270,
    margin      = list(t = 55, b = 60),
    annotations = make_global_annotation(default_idx)
  ) %>%
  config(displayModeBar = FALSE)
```

Column {data-width=420}
-----------------------------------------------------------------------

### τ vs Time Window

How clustering strength changes as the time window varies. Use the dropdown to switch season phase (both outcomes shown simultaneously).

```{r}
p_tau_window <- plot_ly()

disease_colors <- c("DENV-3" = "#2f69b1", "ABV" = "#63b84a")

# Add one trace per disease × season combination (6 total)
# Order: for each season (3), add DENV-3 then ABV → trace indices 1-6
for (s_idx in seq_along(season_levels)) {
  s <- season_levels[s_idx]
  vis_default <- (s_idx == 2)   # default: Mid season

  for (d in c("DENV-3", "ABV")) {
    key       <- paste(d, s, sep = "|")
    tau_vals  <- tau_all[[key]]
    tau_text  <- ifelse(is.na(tau_vals), "NA", sprintf("%.2f", tau_vals))

    p_tau_window <- add_trace(
      p_tau_window,
      x           = windows,
      y           = tau_vals,
      type        = "scatter",
      mode        = "lines+markers",
      name        = d,
      legendgroup = d,
      line        = list(color = disease_colors[d], width = 1.5),
      marker      = list(size = 6, color = disease_colors[d]),
      visible     = vis_default,
      showlegend  = vis_default,
      text        = paste0("Outcome: ", d, "<br>Window: ", windows, " days<br>\u03C4: ", tau_text),
      hoverinfo   = "text"
    )
  }
}

# Each button shows 2 traces for that season, hides the other 4
buttons_season <- lapply(seq_along(season_levels), function(s_idx) {
  vis_vec <- rep(FALSE, 6)
  vis_vec[(2 * s_idx - 1):(2 * s_idx)] <- TRUE
  show_leg <- rep(FALSE, 6)
  show_leg[(2 * s_idx - 1):(2 * s_idx)] <- TRUE

  list(
    method = "update",
    args   = list(list(visible     = as.list(vis_vec),
                       showlegend  = as.list(show_leg))),
    label  = gsub("^\\d+\\. ", "", season_levels[s_idx])
  )
})

p_tau_window %>%
  layout(
    updatemenus = list(list(
      type = "dropdown", x = 0.0, y = 1.15, xanchor = "left",
      buttons = buttons_season, active = 1
    )),
    xaxis      = list(title = "Time Window (days)", tickvals = windows),
    yaxis      = list(title = "\u03C4 (Clustering Ratio)"),
    legend     = list(orientation = "h", y = -0.15),
    height     = 270,
    margin     = list(t = 55)
  ) %>%
  config(displayModeBar = FALSE)
```

### What does "Linked" mean?

```{r}
HTML("
<div style='font-size:15px; line-height:1.6; padding: 4px 2px 0 2px;'>
  <div style='margin-bottom:8px;'><b>Linked pair:</b> Both individuals are test-positive.</div>
  <div><b>Unlinked pair:</b> At least one individual is test-negative.</div>
</div>
")
```


About {data-icon="fa-book-open"}
=======================================================================

Column {data-width=1000}
-----------------------------------------------------------------------

### &nbsp; {.no-title}

```{r}
HTML("
<style>
@import url('https://fonts.googleapis.com/css2?family=DM+Sans:wght@400;500;600;700&family=DM+Mono:wght@500&display=swap');

.about-wrap {
  font-family: 'DM Sans', sans-serif;
  padding: 20px 24px;
  max-width: 1200px;
  margin: 0 auto;
  min-height: 100vh;
}

/* ── Stats row ── */
.stats-row {
  display: grid;
  grid-template-columns: repeat(6, 1fr);
  gap: 10px;
  margin-bottom: 14px;
}
.stat-card {
  background: #fff;
  border-radius: 10px;
  padding: 14px 12px 12px;
  text-align: center;
  border: 1px solid #e4e9f2;
  position: relative;
  overflow: hidden;
}
.stat-card::before {
  content: '';
  position: absolute;
  top: 0; left: 0; right: 0;
  height: 3px;
}
.stat-c1::before { background: #1f3b73; }
.stat-c2::before { background: #2f69b1; }
.stat-c3::before { background: #58b947; }
.stat-c4::before { background: #e53935; }
.stat-c5::before { background: #c27ba0; }
.stat-c6::before { background: #8e7cc3; }
.stat-num { font-size: 22px; font-weight: 700; line-height: 1.1; margin-bottom: 3px; }
.stat-c1 .stat-num { color: #1f3b73; }
.stat-c2 .stat-num { color: #2f69b1; }
.stat-c3 .stat-num { color: #58b947; }
.stat-c4 .stat-num { color: #e53935; }
.stat-c5 .stat-num { color: #c27ba0; }
.stat-c6 .stat-num { color: #8e7cc3; }
.stat-label { font-size: 11px; color: #7a8499; font-weight: 500; }

/* ── Main grid ── */
.main-grid {
  display: grid;
  grid-template-columns: 1fr 1fr 1fr;
  gap: 14px;
}

/* ── Section card ── */
.section-card {
  background: #fff;
  border-radius: 12px;
  border: 1px solid #e4e9f2;
  overflow: hidden;
}
.section-head {
  padding: 10px 16px;
  font-size: 11px;
  font-weight: 700;
  text-transform: uppercase;
  letter-spacing: 0.09em;
  color: #fff;
  display: flex;
  align-items: center;
  gap: 7px;
}
.head-impact  { background: #1f3b73; }
.head-specs   { background: #2c3e5c; }
.head-limits  { background: #374151; }

/* ── Impact ── */
.impact-body {
  padding: 16px;
  font-size: 13.5px;
  line-height: 1.75;
  color: #2d3748;
}

/* ── Spec items ── */
.spec-item {
  padding: 13px 16px;
  border-bottom: 1px solid #f0f3f9;
  display: flex;
  gap: 11px;
  align-items: flex-start;
}
.spec-item:last-child { border-bottom: none; }
.spec-badge {
  font-family: 'DM Mono', monospace;
  font-size: 11px;
  font-weight: 500;
  padding: 2px 7px;
  border-radius: 20px;
  white-space: nowrap;
  flex-shrink: 0;
  margin-top: 1px;
}
.b1 { background: #e8eef8; color: #1f3b73; }
.b2 { background: #e5eef8; color: #2f69b1; }
.b3 { background: #e8f5e4; color: #3a8c2c; }
.b4 { background: #fdf3e3; color: #b07a12; }
.b5 { background: #fde8e8; color: #c0392b; }
.spec-text { font-size: 13px; line-height: 1.6; color: #2d3748; }

/* ── Limitation items ── */
.limit-item {
  padding: 13px 16px;
  border-bottom: 1px solid #f0f3f9;
  display: flex;
  gap: 11px;
  align-items: flex-start;
}
.limit-item:last-child { border-bottom: none; }
.limit-dot {
  width: 10px; height: 10px;
  border-radius: 50%;
  flex-shrink: 0;
  margin-top: 4px;
}
.limit-title { font-size: 13px; font-weight: 700; color: #1e293b; margin-bottom: 3px; }
.limit-desc  { font-size: 12px; line-height: 1.6; color: #5a6a85; }
</style>

<div class='about-wrap'>

  <!-- Stats row -->
  <div class='stats-row'>
    <div class='stat-card stat-c1'>
      <div class='stat-num'>4,461</div>
      <div class='stat-label'>Children Enrolled</div>
    </div>
    <div class='stat-card stat-c2'>
      <div class='stat-num'>50</div>
      <div class='stat-label'>Geo. Clusters</div>
    </div>
    <div class='stat-card stat-c3'>
      <div class='stat-num'>3</div>
      <div class='stat-label'>Epi. Seasons</div>
    </div>
    <div class='stat-card stat-c4'>
      <div class='stat-num' style='font-size:17px;'>2021–2023</div>
      <div class='stat-label'>Study Period</div>
    </div>
    <div class='stat-card stat-c5'>
      <a href='https://clinicaltrials.gov/study/NCT04343521' target='_blank' style='text-decoration:none;'>
        <div class='stat-num' style='font-size:13px;'>NCT04343521 ↗</div>
      </a>
      <div class='stat-label'>Trial Registry</div>
    </div>
    <div class='stat-card stat-c6'>
      <div class='stat-num'>2–15</div>
      <div class='stat-label'>Age Range (yrs)</div>
    </div>
  </div>

  <!-- Main 3-column grid -->
  <div class='main-grid'>

    <!-- Impact -->
    <div class='section-card'>
      <div class='section-head head-impact'>
        <span>📢</span> Real-World Impact
      </div>
      <div class='impact-body'>
        This dashboard analyzes spatiotemporal clustering of Aedes-borne viruses using test-negative design data, revealing whether disease transmission is <strong>localized or fully disseminated</strong>. Findings show that TIRS is most effective during early, highly clustered outbreak phases — guiding public health officials to intervene <em>before</em> community transmission becomes widespread.
      </div>
    </div>

    <!-- Dataset Specs -->
    <div class='section-card'>
      <div class='section-head head-specs'>
        <span>📋</span> Dataset Specifications
      </div>
      <div class='spec-item'>
        <span class='spec-badge b1'>① Source</span>
        <span class='spec-text'>Confidential trial dataset from <a href='https://clinicaltrials.gov/study/NCT04343521' target='_blank' style='color:#2f69b1;font-weight:600;'>NCT04343521</a>, maintained in <strong>REDCap</strong>.</span>
      </div>
      <div class='spec-item'>
        <span class='spec-badge b2'>② Population</span>
        <span class='spec-text'><strong>4,461 children aged 2–15 yrs</strong> across <strong>50 geo. clusters</strong>.</span>
      </div>
      <div class='spec-item'>
        <span class='spec-badge b3'>③ Method</span>
        <span class='spec-text'>Two-arm cluster-RCT; weekly surveillance via home visits, calls &amp; SMS + <strong>PCR &amp; IgM</strong> testing.</span>
      </div>
      <div class='spec-item'>
        <span class='spec-badge b4'>④ Location</span>
        <span class='spec-text'>Aedes hotspot in <strong>Mérida, Yucatan, Mexico</strong>.</span>
      </div>
      <div class='spec-item'>
        <span class='spec-badge b5'>⑤ Period</span>
        <span class='spec-text'>Three epi. seasons: <strong>Jul 1, 2021 – Dec 31, 2023</strong>.</span>
      </div>
    </div>

    <!-- Limitations -->
    <div class='section-card'>
      <div class='section-head head-limits'>
        <span>⚠</span> Study Limitations
      </div>
      <div class='limit-item'>
        <div class='limit-dot' style='background:#e53935;'></div>
        <div>
          <div class='limit-title'>Secondary Analysis</div>
          <div class='limit-desc'>Constrained by original trial design, limiting adaptation for new research questions.</div>
        </div>
      </div>
      <div class='limit-item'>
        <div class='limit-dot' style='background:#e5a823;'></div>
        <div>
          <div class='limit-title'>Statistical Power</div>
          <div class='limit-desc'>DENV-3 decline required expanding to ABV, possibly obscuring individual virus dynamics.</div>
        </div>
      </div>
      <div class='limit-item'>
        <div class='limit-dot' style='background:#2f69b1;'></div>
        <div>
          <div class='limit-title'>Temporal Generalizability</div>
          <div class='limit-desc'>2023 was anomalously high-transmission; patterns may not apply to standard seasons.</div>
        </div>
      </div>
      <div class='limit-item'>
        <div class='limit-dot' style='background:#1f3b73;'></div>
        <div>
          <div class='limit-title'>Intervention Threshold</div>
          <div class='limit-desc'>TIRS is timing-sensitive; once transmission shifts citywide, community-level action alone is insufficient.</div>
        </div>
      </div>
    </div>

  </div>
</div>
")
```
