---
title: 'Targeted Indoor Residual Spraying (TIRS) Effectiveness in Mérida, 2023'
author: "Yining(Carina) Fu"
output: 
    flexdashboard::flex_dashboard:
      orientation: columns
      vertical_layout: fill
      navbar:
        - { title: "GitHub", href: "https://github.com/yiningfu619/SpatiotemporalAnalysis", align: right, icon: "fa-github" }
        - { title: "Source Code", href: "https://github.com/yiningfu619/SpatiotemporalAnalysis/blob/main/index.Rmd", align: right, icon: "fa-code" }
theme: cosmo

---

```{r setup, include=FALSE}
# ==========================================
# Load required packages (shiny removed)
# ==========================================
library(flexdashboard)
library(htmltools)
library(dplyr)
library(ggplot2)
library(lubridate)
library(tidyr)
library(scales)
library(plotly)
library(DT)

tnd.tirs <- read.csv("/Users/fuyi/Library/CloudStorage/OneDrive-Emory/DATA555/tnd_tirs_data.csv")
```

```{css}
.chart-stage,
.section.level3,
.sidebar {
  overflow: visible !important;
}

.chart-wrapper {
  border-radius: 10px;
  border: 1px solid #d9d9d9;
  box-shadow: 0 1px 2px rgba(0,0,0,0.04);
  background: #ffffff;
}

.chart-title {
  font-weight: 700;
  color: #1f3b73;
}

.small-note {
  color: #6b7280;
  font-size: 15px;
  margin-top: -6px;
  margin-bottom: 12px;
}

/* ===== Tau card ===== */
.tau-card-final {
  background: linear-gradient(180deg, #ef5350 0%, #e53935 100%);
  color: white;
  border-radius: 10px;
  padding: 16px 18px 14px 18px;
  min-height: 120px;
  box-shadow: 0 2px 6px rgba(0,0,0,0.08);
  margin-top: 0;
  text-align: center;
}

.tau-main-line {
  font-size: 34px;
  font-weight: 800;
  line-height: 1.1;
  margin-bottom: 10px;
}

.tau-mid-line {
  font-size: 20px;
  font-weight: 700;
  line-height: 1.2;
  margin-bottom: 10px;
}

.tau-bottom-line {
  font-size: 14px;
  font-weight: 600;
  line-height: 1.2;
  opacity: 0.98;
}

/* hide tau panel title, but keep the panel itself */
.tau-panel .chart-title {
  display: none !important;
}

/* give tau panel a little breathing room without pushing upward */
.tau-panel .chart-stage {
  padding-top: 14px !important;
  padding-bottom: 6px !important;
}

/* stop weird collapsing behavior */
.tau-panel .chart-wrapper {
  min-height: auto !important;
}

/* ===== Interpretation card ===== */
.interp-card {
  background: #eaf3fb;
  border-radius: 10px;
  padding: 18px;
  min-height: 190px;
  border: 1px solid #d9e7f6;
}

/* ===== Footer note ===== */
.results-note {
  color: #6b7280;
  font-size: 15px;
  margin-top: 6px;
}

table {
  font-size: 15px;
}
```

```{r data-clean, include=FALSE}
# ==========================================
# Data cleaning, extract Year column explicitly
# ==========================================
clean_df <- tnd.tirs %>%
  mutate(
    var6_pcr_date = as.character(var6_pcr_date),
    var6_pcr_date = na_if(var6_pcr_date, ""),
    Date = suppressWarnings(mdy(var6_pcr_date)),
    Year = year(Date)
  ) 

# ==========================================
# Generate base summary data (keep all 0s, handle Year labels)
# ==========================================
summary_base <- clean_df %>%
  group_by(Year) %>%
  summarise(
    DENV = sum(var6_pcr_res___1 == "Checked", na.rm = TRUE),
    ZIKV = sum(var6_pcr_res___2 == "Checked", na.rm = TRUE),
    CHIKV = sum(var6_pcr_res___3 == "Checked", na.rm = TRUE),
    .groups = "drop" 
  ) %>%
  mutate(Year = ifelse(is.na(Year), "Unknown", as.character(Year)))

# ==========================================
# Prepare data for [Bar Chart]
# ==========================================
summary_data_bar <- summary_base %>%
  pivot_longer(cols = c(DENV, ZIKV, CHIKV), names_to = "Virus", values_to = "Count") %>%
  filter(Count > 0) %>% 
  group_by(Year) %>%
  mutate(
    Prop = Count / sum(Count),
    Label = paste0(Virus, "\n", Count, "\n(", percent(Prop, accuracy = 0.1), ")")
  ) %>%
  ungroup()
```

Background {data-icon="fa-chalkboard"}
=======================================================================

Column {.sidebar data-width=200}
-----------------------------------------------------------------------

### 📌 Data Note
> All tables and figures presented on this page are derived from the test-negative design (TND) subset, representing a specific analytical cohort rather than the raw overall population.

Column {data-width="500"}
---------------------------------

### Data Summary Table

```{r}
# ==========================================
# Prepare and generate data for [Table] (including Total)
# ==========================================
table_data <- summary_base %>%
  mutate(Total = DENV + ZIKV + CHIKV) %>%
  bind_rows(
    summarise(., 
      Year = "Total",
      DENV = sum(DENV, na.rm = TRUE),
      ZIKV = sum(ZIKV, na.rm = TRUE),
      CHIKV = sum(CHIKV, na.rm = TRUE),
      Total = sum(Total, na.rm = TRUE)
    )
  )

knitr::kable(table_data, align = "c")
```


### 2023 DENV-3 Summary

```{r}
# ---------------------------------------------------------
# Prepare 2023 DENV-3 Season Data (Jul-Dec, exact months)
# ---------------------------------------------------------
df_denv3_bg <- tnd.tirs %>% 
  mutate(participant_id = paste0(record_id, "_", rn2_pt_id)) %>%
  dplyr::select(participant_id, cl_nr, rn1_br, var6_symp_date, var6_abv_pos___1, var6_denv_type___3) %>%
  mutate(
    cluster = as.character(cl_nr),
    illness_onset = as.Date(var6_symp_date, format = "%m/%d/%Y"),
    intervention = factor(rn1_br, levels = c(1, 2), labels = c("Control", "TIRS")),
    is_case = as.numeric(var6_abv_pos___1),
    is_denv3 = case_when(
      as.character(var6_denv_type___3) %in% c("Checked", "1") ~ 1,
      is_case == 0 ~ 0,
      TRUE ~ NA_real_
    )
  ) %>%
  filter(illness_onset >= as.Date("2023-07-01") & illness_onset <= as.Date("2023-12-31")) %>%
  drop_na(illness_onset, cluster, intervention, is_denv3) %>%
  distinct(participant_id, illness_onset, .keep_all = TRUE)
```

```{r}
plot_data <- df_denv3_bg %>%
  filter(is_denv3 == 1)

weekly_counts <- plot_data %>%
  mutate(Week = floor_date(illness_onset, unit = "week", week_start = 1)) %>%
  count(Week, name = "Weekly_Cases") %>%
  tidyr::complete(
    Week = seq(
      floor_date(as.Date("2023-07-01"), unit = "week", week_start = 1),
      floor_date(as.Date("2023-12-31"), unit = "week", week_start = 1),
      by = "1 week"
    ),
    fill = list(Weekly_Cases = 0)
  ) %>%
  mutate(
    Week_End = Week + 6,
    hover_text = paste0(
      "Week: ", format(Week, "%b %d"), " - ", format(Week_End, "%b %d, %Y"), "\n",
      "Cases: ", Weekly_Cases
    )
  )

p_weekly_smooth <- ggplot() +
  geom_col(
    data = weekly_counts,
    aes(x = Week, y = Weekly_Cases, text = hover_text),
    fill = "#56B4E9", width = 6, color = "white", alpha = 0.8
  ) +
  geom_smooth(
    data = weekly_counts,
    aes(x = Week, y = Weekly_Cases),
    method = "loess", span = 0.35, se = FALSE,
    color = "#E69F00", linewidth = 1.2
  ) +
  scale_x_date(
    limits = c(as.Date("2023-06-26"), as.Date("2024-01-07")),
    breaks = seq(as.Date("2023-07-03"), as.Date("2023-12-25"), by = "2 weeks"),
    date_labels = "%b %d"
  ) +
  theme_minimal() +
  labs(
    x = "Week of Illness Onset",
    y = "Number of DENV-3 Cases",
    title = "DENV-3 Weekly Case Distribution (Jul-Dec 2023)"
  ) +
  theme(
    axis.text.x = element_text(size = 10, angle = 45, hjust = 1),
    axis.text.y = element_text(size = 11),
    panel.grid.minor = element_blank()
  )

ggplotly(p_weekly_smooth, tooltip = "text")
```

> The monthly distribution reveals a sharp peak in DENV-3 cases during August 2023, reaching 15 cases. Following this sudden spike, the case count rapidly declined, with zero new cases reported from September 2023 through January 2024.


Column {data-width="500"}
---------------------------------

### Age of Participants in Each Block

```{r}
df_unique <- clean_df %>%
  distinct(record_id, .keep_all = TRUE)

df_unique <- df_unique %>%
  mutate(
    age = as.numeric(Age),
    Block_Type = factor(Block.Type)
  ) %>%
  group_by(Block_Type) %>%
  mutate(Block_Label = paste0(Block_Type, "\n(n=", n(), ")")) %>%
  ungroup()

p <- ggplot(df_unique, aes(
  x = Block_Label,
  y = Age,
  fill = Block_Type,
  text = paste("ID:", record_id, "<br>Age:", age)
)) +
  geom_boxplot(outlier.alpha = 0.3) +
  geom_jitter(width = 0.15, alpha = 0.3, size = 1) +
  theme_minimal() +
  labs(x = "Block Type", y = "Age", fill = "Block Type")

ggplotly(p, tooltip = "text")
```

> The boxplots indicate that participant age distributions are highly comparable between the Central and Periphery blocks, with both exhibiting a median age around 10 years. Additionally, the plot shows that the External block contains only a single data point (n=1), which prevents a meaningful comparison of its distribution.


TAU {data-icon="fa-chart-simple"}
=======================================================================

```{r tau-prep, include=FALSE}
# ---------------------------
# DENV-3 DATA
# ---------------------------
df_denv3_season <- tnd.tirs %>%
  mutate(participant_id = paste0(record_id, "_", rn2_pt_id)) %>%
  mutate(
    cluster = as.character(cl_nr),
    illness_onset = as.Date(var6_symp_date, format = "%m/%d/%Y"),
    intervention = factor(rn1_br, levels = c(1,2), labels = c("Control","TIRS")),
    is_case = as.numeric(var6_abv_pos___1),
    is_denv3 = case_when(
      as.character(var6_denv_type___3) %in% c("Checked","1") ~ 1,
      is_case == 0 ~ 0,
      TRUE ~ NA_real_
    ),
    Season_Part = case_when(
      illness_onset >= as.Date("2023-07-01") & illness_onset < as.Date("2023-09-01") ~ "1. Early (Jul-Aug)",
      illness_onset >= as.Date("2023-09-01") & illness_onset < as.Date("2023-11-01") ~ "2. Mid (Sep-Oct)",
      illness_onset >= as.Date("2023-11-01") & illness_onset <= as.Date("2023-12-31") ~ "3. Late (Nov-Dec)",
      TRUE ~ NA_character_
    )
  ) %>%
  filter(!is.na(Season_Part)) %>%
  drop_na(illness_onset, cluster, intervention, is_denv3) %>%
  distinct(participant_id, illness_onset, .keep_all = TRUE)

# ---------------------------
# ABV DATA
# ---------------------------
df_tau_ready <- tnd.tirs %>%
  mutate(participant_id = paste0(record_id, "_", rn2_pt_id)) %>%
  mutate(
    cluster = as.character(cl_nr),
    illness_onset = as.Date(var6_symp_date, format = "%m/%d/%Y"),
    intervention = factor(rn1_br, levels = c(1,2), labels = c("Control","TIRS")),
    is_case = as.numeric(var6_abv_pos___1),
    Season_Part = case_when(
      illness_onset >= as.Date("2023-07-01") & illness_onset < as.Date("2023-09-01") ~ "1. Early (Jul-Aug)",
      illness_onset >= as.Date("2023-09-01") & illness_onset < as.Date("2023-11-01") ~ "2. Mid (Sep-Oct)",
      illness_onset >= as.Date("2023-11-01") & illness_onset <= as.Date("2023-12-31") ~ "3. Late (Nov-Dec)",
      TRUE ~ NA_character_
    )
  ) %>%
  drop_na(illness_onset, cluster, is_case, intervention, Season_Part) %>%
  distinct(participant_id, illness_onset, .keep_all = TRUE)

# ---------------------------
# DENV-3 tau function
# ---------------------------
calculate_denv3_tau <- function(df, t_window = 30) {
  n <- nrow(df)
  if (n < 2) {
    return(data.frame(
      `Neighborhood Pairs (Both Positive)` = NA,
      `Neighborhood Pairs (At least 1 Negative)` = NA,
      `Neighborhood Odds` = NA,
      `Citywide Pairs (Both Positive)` = NA,
      `Citywide Pairs (At least 1 Negative)` = NA,
      `Citywide Odds` = NA,
      `Clustering Ratio (Tau)` = NA,
      check.names = FALSE
    ))
  }
  time_mat   <- abs(outer(as.numeric(df$illness_onset), as.numeric(df$illness_onset), "-")) <= t_window
  cluster_mat <- outer(df$cluster, df$cluster, "==")
  linked_mat  <- outer(df$is_denv3 == 1, df$is_denv3 == 1, "&")
  person_mat  <- outer(df$participant_id, df$participant_id, "==")
  time_valid  <- time_mat & upper.tri(time_mat) & !person_mat
  local_pairs_mask  <- time_valid & cluster_mat
  a_local  <- sum(local_pairs_mask & linked_mat)
  b_local  <- sum(local_pairs_mask & !linked_mat)
  theta_cluster   <- ifelse(b_local == 0, NA, a_local / b_local)
  global_pairs_mask <- time_valid
  a_global  <- sum(global_pairs_mask & linked_mat)
  b_global  <- sum(global_pairs_mask & !linked_mat)
  theta_anywhere  <- ifelse(b_global == 0, NA, a_global / b_global)
  tau <- ifelse(
    is.na(theta_cluster) | is.na(theta_anywhere) | theta_anywhere == 0,
    NA, theta_cluster / theta_anywhere
  )
  data.frame(
    `Neighborhood Pairs (Both Positive)` = a_local,
    `Neighborhood Pairs (At least 1 Negative)` = b_local,
    `Neighborhood Odds` = theta_cluster,
    `Citywide Pairs (Both Positive)` = a_global,
    `Citywide Pairs (At least 1 Negative)` = b_global,
    `Citywide Odds` = theta_anywhere,
    `Clustering Ratio (Tau)` = tau,
    check.names = FALSE
  )
}

# ---------------------------
# ABV tau function
# ---------------------------
calculate_new_tau <- function(df, t_window = 30) {
  if (nrow(df) < 2) {
    return(data.frame(
      `Neighborhood Pairs (Both Positive)` = NA,
      `Neighborhood Pairs (At least 1 Negative)` = NA,
      `Neighborhood Odds` = NA,
      `Citywide Pairs (Both Positive)` = NA,
      `Citywide Pairs (At least 1 Negative)` = NA,
      `Citywide Odds` = NA,
      `Clustering Ratio (Tau)` = NA,
      check.names = FALSE
    ))
  }
  time_mat    <- abs(outer(as.numeric(df$illness_onset), as.numeric(df$illness_onset), "-")) <= t_window
  cluster_mat <- outer(df$cluster, df$cluster, "==")
  linked_mat  <- outer(df$is_case == 1, df$is_case == 1, "&")
  person_mat  <- outer(df$participant_id, df$participant_id, "==")
  time_valid  <- time_mat & upper.tri(time_mat) & !person_mat
  local_pairs_mask  <- time_valid & cluster_mat
  a_local  <- sum(local_pairs_mask & linked_mat)
  b_local  <- sum(local_pairs_mask & !linked_mat)
  theta_cluster   <- ifelse(b_local == 0, NA, a_local / b_local)
  global_pairs_mask <- time_valid
  a_global  <- sum(global_pairs_mask & linked_mat)
  b_global  <- sum(global_pairs_mask & !linked_mat)
  theta_anywhere  <- ifelse(b_global == 0, NA, a_global / b_global)
  tau <- ifelse(
    is.na(theta_cluster) | is.na(theta_anywhere) | theta_anywhere == 0,
    NA, theta_cluster / theta_anywhere
  )
  data.frame(
    `Neighborhood Pairs (Both Positive)` = a_local,
    `Neighborhood Pairs (At least 1 Negative)` = b_local,
    `Neighborhood Odds` = theta_cluster,
    `Citywide Pairs (Both Positive)` = a_global,
    `Citywide Pairs (At least 1 Negative)` = b_global,
    `Citywide Odds` = theta_anywhere,
    `Clustering Ratio (Tau)` = tau,
    check.names = FALSE
  )
}

# ---------------------------
# Pre-compute all combinations
# ---------------------------
season_levels <- c("1. Early (Jul-Aug)", "2. Mid (Sep-Oct)", "3. Late (Nov-Dec)")
windows       <- seq(7, 60, by = 7)
default_window <- 30

combos <- expand.grid(
  disease = c("DENV-3", "ABV"),
  season  = season_levels,
  stringsAsFactors = FALSE
)

# Results at default window (for odds charts and tau summary table)
odds_data <- lapply(seq_len(nrow(combos)), function(i) {
  d <- combos$disease[i]; s <- combos$season[i]
  df  <- if (d == "DENV-3") df_denv3_season %>% filter(Season_Part == s) else df_tau_ready %>% filter(Season_Part == s)
  res <- if (d == "DENV-3") calculate_denv3_tau(df, default_window) else calculate_new_tau(df, default_window)
  list(
    local_linked    = res$`Neighborhood Pairs (Both Positive)`[[1]],
    local_unlinked  = res$`Neighborhood Pairs (At least 1 Negative)`[[1]],
    global_linked   = res$`Citywide Pairs (Both Positive)`[[1]],
    global_unlinked = res$`Citywide Pairs (At least 1 Negative)`[[1]],
    local_odds      = res$`Neighborhood Odds`[[1]],
    global_odds     = res$`Citywide Odds`[[1]],
    tau             = res$`Clustering Ratio (Tau)`[[1]]
  )
})
names(odds_data) <- paste(combos$disease, combos$season, sep = "|")

# Tau values across all windows (for tau vs time window chart)
tau_all <- lapply(seq_len(nrow(combos)), function(i) {
  d <- combos$disease[i]; s <- combos$season[i]
  sapply(windows, function(w) {
    df  <- if (d == "DENV-3") df_denv3_season %>% filter(Season_Part == s) else df_tau_ready %>% filter(Season_Part == s)
    res <- if (d == "DENV-3") calculate_denv3_tau(df, w) else calculate_new_tau(df, w)
    res$`Clustering Ratio (Tau)`[[1]]
  })
})
names(tau_all) <- paste(combos$disease, combos$season, sep = "|")

# Default combo index (DENV-3, Mid season)
default_idx <- which(combos$disease == "DENV-3" & combos$season == "2. Mid (Sep-Oct)")
```

Column {data-width=280}
-----------------------------------------------------------------------

### Controls

```{r}
HTML("
<div style='font-size:14px; color:#374151; line-height:1.8; padding:4px 2px;'>
  <p>Use the <b>dropdown menus</b> embedded in each chart to switch between outcomes and season phases.</p>
  <hr style='margin:8px 0; border-color:#e5e7eb;'>
  <p><b>Outcome:</b> DENV-3 or Aedes-borne diseases (ABV)</p>
  <p><b>Season phase:</b><br>
    &nbsp;• Early (Jul–Aug)<br>
    &nbsp;• Mid (Sep–Oct)<br>
    &nbsp;• Late (Nov–Dec)
  </p>
  <p><b>Time window:</b> Odds charts are fixed at <b>30 days</b>. The τ vs Time Window chart shows all windows (7–60 days).</p>
</div>
")
```

### τ Summary (Window = 30 days)

```{r}
tau_summary_df <- data.frame(
  Disease = combos$disease,
  Season  = gsub("^\\d+\\. ", "", combos$season),
  `τ`     = sapply(odds_data, function(x) ifelse(is.na(x$tau), "—", sprintf("%.3f", x$tau))),
  Result  = sapply(odds_data, function(x) {
    if (is.na(x$tau))    "Insufficient pairs"
    else if (x$tau > 1)  "Clustering detected"
    else if (x$tau == 1) "No difference"
    else                 "Weak clustering"
  }),
  check.names = FALSE
)

DT::datatable(
  tau_summary_df,
  options = list(pageLength = 6, dom = "t", ordering = FALSE),
  rownames = FALSE
) %>%
  DT::formatStyle(
    "Result",
    backgroundColor = DT::styleEqual(
      c("Clustering detected", "Weak clustering", "Insufficient pairs"),
      c("#d1fae5", "#fef3c7", "#f3f4f6")
    )
  )
```

Column {data-width=500}
-----------------------------------------------------------------------

### Local Odds (Within Cluster)

Pairs of individuals in the **same cluster** within the time window (30 days). Use the dropdown to switch outcome / season.

```{r}
p_local <- plot_ly()

for (i in seq_len(nrow(combos))) {
  d   <- combos$disease[i]; s <- combos$season[i]
  key <- paste(d, s, sep = "|")
  od  <- odds_data[[key]]
  vis <- (i == default_idx)
  counts <- c(od$local_linked, od$local_unlinked)
  counts[is.na(counts)] <- 0

  p_local <- add_trace(
    p_local,
    x    = c("Linked", "Unlinked"),
    y    = counts,
    type = "bar",
    name = paste(d, gsub("^\\d+\\. ", "", s), sep = " | "),
    visible    = vis,
    showlegend = FALSE,
    marker     = list(color = c("#2f69b1", "#a9c2df")),
    text       = paste0(c("Linked", "Unlinked"), ": ", comma(counts)),
    hoverinfo  = "text"
  )
}

make_local_annotation <- function(i) {
  lo  <- odds_data[[paste(combos$disease[i], combos$season[i], sep = "|")]]$local_odds
  txt <- if (is.na(lo)) "Neighborhood Odds = NA" else paste0("<b>Neighborhood Odds = ", sprintf("%.2f", lo), "</b>")
  list(list(x = 0.5, y = -0.22, xref = "paper", yref = "paper",
            text = txt, showarrow = FALSE, font = list(size = 13)))
}

buttons_local <- lapply(seq_len(nrow(combos)), function(i) {
  vis <- rep(FALSE, nrow(combos)); vis[i] <- TRUE
  list(
    method = "update",
    args   = list(list(visible = as.list(vis)),
                  list(annotations = make_local_annotation(i))),
    label  = paste(combos$disease[i], gsub("^\\d+\\. ", "", combos$season[i]), sep = " | ")
  )
})

p_local %>%
  layout(
    updatemenus = list(list(
      type = "dropdown", x = 0.0, y = 1.20, xanchor = "left",
      buttons = buttons_local, active = default_idx - 1
    )),
    xaxis       = list(title = ""),
    yaxis       = list(title = "Pair Count"),
    showlegend  = FALSE,
    height      = 270,
    margin      = list(t = 55, b = 60),
    annotations = make_local_annotation(default_idx)
  ) %>%
  config(displayModeBar = FALSE)
```

### Baseline Odds (Anywhere)

Pairs of individuals **anywhere in the city** within the time window (30 days). Use the dropdown to switch outcome / season.

```{r}
p_global <- plot_ly()

for (i in seq_len(nrow(combos))) {
  d   <- combos$disease[i]; s <- combos$season[i]
  key <- paste(d, s, sep = "|")
  od  <- odds_data[[key]]
  vis <- (i == default_idx)
  counts <- c(od$global_linked, od$global_unlinked)
  counts[is.na(counts)] <- 0

  p_global <- add_trace(
    p_global,
    x    = c("Linked", "Unlinked"),
    y    = counts,
    type = "bar",
    name = paste(d, gsub("^\\d+\\. ", "", s), sep = " | "),
    visible    = vis,
    showlegend = FALSE,
    marker     = list(color = c("#58b947", "#b7d9ad")),
    text       = paste0(c("Linked", "Unlinked"), ": ", comma(counts)),
    hoverinfo  = "text"
  )
}

make_global_annotation <- function(i) {
  go  <- odds_data[[paste(combos$disease[i], combos$season[i], sep = "|")]]$global_odds
  txt <- if (is.na(go)) "Citywide Odds = NA" else paste0("<b>Citywide Odds = ", sprintf("%.2f", go), "</b>")
  list(list(x = 0.5, y = -0.22, xref = "paper", yref = "paper",
            text = txt, showarrow = FALSE, font = list(size = 13)))
}

buttons_global <- lapply(seq_len(nrow(combos)), function(i) {
  vis <- rep(FALSE, nrow(combos)); vis[i] <- TRUE
  list(
    method = "update",
    args   = list(list(visible = as.list(vis)),
                  list(annotations = make_global_annotation(i))),
    label  = paste(combos$disease[i], gsub("^\\d+\\. ", "", combos$season[i]), sep = " | ")
  )
})

p_global %>%
  layout(
    updatemenus = list(list(
      type = "dropdown", x = 0.0, y = 1.20, xanchor = "left",
      buttons = buttons_global, active = default_idx - 1
    )),
    xaxis       = list(title = ""),
    yaxis       = list(title = "Pair Count"),
    showlegend  = FALSE,
    height      = 270,
    margin      = list(t = 55, b = 60),
    annotations = make_global_annotation(default_idx)
  ) %>%
  config(displayModeBar = FALSE)
```

Column {data-width=420}
-----------------------------------------------------------------------

### τ vs Time Window

How clustering strength changes as the time window varies. Use the dropdown to switch season phase (both outcomes shown simultaneously).

```{r}
p_tau_window <- plot_ly()

disease_colors <- c("DENV-3" = "#2f69b1", "ABV" = "#63b84a")

# Add one trace per disease × season combination (6 total)
# Order: for each season (3), add DENV-3 then ABV → trace indices 1-6
for (s_idx in seq_along(season_levels)) {
  s <- season_levels[s_idx]
  vis_default <- (s_idx == 2)   # default: Mid season

  for (d in c("DENV-3", "ABV")) {
    key       <- paste(d, s, sep = "|")
    tau_vals  <- tau_all[[key]]
    tau_text  <- ifelse(is.na(tau_vals), "NA", sprintf("%.2f", tau_vals))

    p_tau_window <- add_trace(
      p_tau_window,
      x           = windows,
      y           = tau_vals,
      type        = "scatter",
      mode        = "lines+markers",
      name        = d,
      legendgroup = d,
      line        = list(color = disease_colors[d], width = 1.5),
      marker      = list(size = 6, color = disease_colors[d]),
      visible     = vis_default,
      showlegend  = vis_default,
      text        = paste0("Outcome: ", d, "<br>Window: ", windows, " days<br>\u03C4: ", tau_text),
      hoverinfo   = "text"
    )
  }
}

# Each button shows 2 traces for that season, hides the other 4
buttons_season <- lapply(seq_along(season_levels), function(s_idx) {
  vis_vec <- rep(FALSE, 6)
  vis_vec[(2 * s_idx - 1):(2 * s_idx)] <- TRUE
  show_leg <- rep(FALSE, 6)
  show_leg[(2 * s_idx - 1):(2 * s_idx)] <- TRUE

  list(
    method = "update",
    args   = list(list(visible     = as.list(vis_vec),
                       showlegend  = as.list(show_leg))),
    label  = gsub("^\\d+\\. ", "", season_levels[s_idx])
  )
})

p_tau_window %>%
  layout(
    updatemenus = list(list(
      type = "dropdown", x = 0.0, y = 1.15, xanchor = "left",
      buttons = buttons_season, active = 1
    )),
    xaxis      = list(title = "Time Window (days)", tickvals = windows),
    yaxis      = list(title = "\u03C4 (Clustering Ratio)"),
    legend     = list(orientation = "h", y = -0.15),
    height     = 270,
    margin     = list(t = 55)
  ) %>%
  config(displayModeBar = FALSE)
```

### What does "Linked" mean?

```{r}
HTML("
<div style='font-size:15px; line-height:1.6; padding: 4px 2px 0 2px;'>
  <div style='margin-bottom:8px;'><b>Linked pair:</b> Both individuals are test-positive.</div>
  <div><b>Unlinked pair:</b> At least one individual is test-negative.</div>
</div>
")
```


About {data-icon="fa-book-open"}
=======================================================================

Column {data-width=200}
-----------------------------------------------------------------------

### &nbsp;

```{r}
HTML("
<div style='display:flex; flex-direction:column; gap:14px; padding: 8px 4px;'>

  <div style='background:#1f3b73; color:white; border-radius:10px; padding:18px 16px; text-align:center;'>
    <div style='font-size:36px; font-weight:800; line-height:1;'>4,461</div>
    <div style='font-size:13px; margin-top:6px; opacity:0.9;'>Children Enrolled</div>
  </div>

  <div style='background:#2f69b1; color:white; border-radius:10px; padding:18px 16px; text-align:center;'>
    <div style='font-size:36px; font-weight:800; line-height:1;'>50</div>
    <div style='font-size:13px; margin-top:6px; opacity:0.9;'>Geographic Clusters</div>
  </div>

  <div style='background:#58b947; color:white; border-radius:10px; padding:18px 16px; text-align:center;'>
    <div style='font-size:36px; font-weight:800; line-height:1;'>3</div>
    <div style='font-size:13px; margin-top:6px; opacity:0.9;'>Epidemiological Seasons</div>
  </div>

  <div style='background:#e53935; color:white; border-radius:10px; padding:18px 16px; text-align:center;'>
    <div style='font-size:15px; font-weight:800; line-height:1.3;'>2021 – 2023</div>
    <div style='font-size:13px; margin-top:6px; opacity:0.9;'>Study Period</div>
  </div>
  
  <div style='background:#e5a823; color:white; border-radius:10px; padding:18px 16px; text-align:center;'>
    <a href='[https://clinicaltrials.gov/study/NCT04343521](https://clinicaltrials.gov/study/NCT04343521)' target='_blank' style='color:white; text-decoration:none;'>
      <div style='font-size:18px; font-weight:800; line-height:1.2;'>NCT04343521 ↗</div>
    </a>
    <div style='font-size:13px; margin-top:6px; opacity:0.9;'>Trial Registry</div>
  </div>

  <div style='background:#0288d1; color:white; border-radius:10px; padding:18px 16px; text-align:center;'>
    <div style='font-size:36px; font-weight:800; line-height:1;'>2 – 15</div>
    <div style='font-size:13px; margin-top:6px; opacity:0.9;'>Age Range (years)</div>
  </div>

</div>
")
```

Column {data-width=550}
-----------------------------------------------------------------------

### Research Overview & Significance

```{r}
HTML("
<div style='max-width:720px; padding: 4px;'>

  <div style='margin-bottom: 28px;'>
    <div style='background: #1f3b73; color: white; border-radius: 10px 10px 0 0; padding: 12px 20px; font-weight: 800; font-size: 16px; letter-spacing: 0.05em; display: flex; align-items: center; gap: 8px;'>
      <span style='font-size: 18px;'>📢</span> REAL-WORLD IMPACT & IMPORTANCE
    </div>
    <div style='background: #ffffff; border: 2px solid #1f3b73; border-top: none; border-radius: 0 0 10px 10px; padding: 20px; box-shadow: 0 6px 12px rgba(0,0,0,0.08);'>
      <div style='font-size: 15px; line-height: 1.8; color: #1e293b; font-weight: 500;'>
        This interactive dashboard provides a framework for analyzing the spatiotemporal clustering of Aedes-borne viruses using test-negative design data, allowing users to determine whether disease transmission is localized or fully disseminated. By revealing that targeted indoor residual spraying (TIRS) is most effective during the early, highly clustered phases of an outbreak, these findings guide public health officials to deploy rapid interventions before community transmission becomes widespread.
      </div>
    </div>
  </div>

  <div style='height: 1px; background: #e2e8f0; margin-bottom: 24px; position: relative;'>
    <span style='position: absolute; top: -10px; left: 20px; background: white; padding: 0 10px; color: #94a3b8; font-size: 12px; font-weight: 700; text-transform: uppercase;'>Dataset Specifications</span>
  </div>

  <div style='display:flex; flex-direction:column; gap:10px;'>

    <div style='display:flex; align-items:flex-start; gap:12px;'>
      <div style='min-width:32px; height:32px; background:#1f3b73; border-radius:50%; display:flex; align-items:center; justify-content:center; color:white; font-weight:700; font-size:14px; flex-shrink:0; margin-top:2px;'>1</div>
      <div style='background:#f8fafc; border:1px solid #e2e8f0; border-radius:8px; padding:10px 14px; font-size:14px; line-height:1.5; color:#1e293b;'>
        <b>Data Source &amp; Access:</b> The primary data source is a confidential trial-level dataset derived from a registered clinical trial
        (<a href='https://clinicaltrials.gov/study/NCT04343521' target='_blank' style='color:#2f69b1;'>NCT04343521</a>)
        and securely maintained in a <b>REDCap</b> database.
      </div>
    </div>

    <div style='display:flex; align-items:flex-start; gap:12px;'>
      <div style='min-width:32px; height:32px; background:#2f69b1; border-radius:50%; display:flex; align-items:center; justify-content:center; color:white; font-weight:700; font-size:14px; flex-shrink:0; margin-top:2px;'>2</div>
      <div style='background:#f8fafc; border:1px solid #e2e8f0; border-radius:8px; padding:10px 14px; font-size:14px; line-height:1.5; color:#1e293b;'>
        <b>Study Population:</b> The study population comprised <b>4,461 children aged 2–15 years</b> who were monitored across <b>50 geographical clusters</b>.
      </div>
    </div>

    <div style='display:flex; align-items:flex-start; gap:12px;'>
      <div style='min-width:32px; height:32px; background:#58b947; border-radius:50%; display:flex; align-items:center; justify-content:center; color:white; font-weight:700; font-size:14px; flex-shrink:0; margin-top:2px;'>3</div>
      <div style='background:#f8fafc; border:1px solid #e2e8f0; border-radius:8px; padding:10px 14px; font-size:14px; line-height:1.5; color:#1e293b;'>
        <b>Data Collection Method:</b> Data were prospectively collected via a <b>two-arm, parallel, unblinded, cluster-randomized trial</b> utilizing active weekly surveillance — including rotating home visits, phone calls, and SMS messaging — alongside laboratory <b>PCR and IgM testing</b> to confirm symptomatic infections.
      </div>
    </div>

    <div style='display:flex; align-items:flex-start; gap:12px;'>
      <div style='min-width:32px; height:32px; background:#e5a823; border-radius:50%; display:flex; align-items:center; justify-content:center; color:white; font-weight:700; font-size:14px; flex-shrink:0; margin-top:2px;'>4</div>
      <div style='background:#f8fafc; border:1px solid #e2e8f0; border-radius:8px; padding:10px 14px; font-size:14px; line-height:1.5; color:#1e293b;'>
        <b>Study Location:</b> The research was conducted in an <b>Aedes-borne disease hotspot</b> located in <b>Mérida, Yucatan State, Mexico</b>.
      </div>
    </div>

    <div style='display:flex; align-items:flex-start; gap:12px;'>
      <div style='min-width:32px; height:32px; background:#e53935; border-radius:50%; display:flex; align-items:center; justify-content:center; color:white; font-weight:700; font-size:14px; flex-shrink:0; margin-top:2px;'>5</div>
      <div style='background:#f8fafc; border:1px solid #e2e8f0; border-radius:8px; padding:10px 14px; font-size:14px; line-height:1.5; color:#1e293b;'>
        <b>Time Period:</b> Data collection spanned three distinct epidemiological seasons, actively monitoring the pediatric cohort from <b>July 1, 2021 to December 31, 2023</b>.
      </div>
    </div>

  </div>
</div>
")
```

Column {data-width=250}
-----------------------------------------------------------------------
### Study Limitations

```{r}
HTML("
<div style='display:flex; flex-direction:column; gap:12px;'>
    
    <div style='background:#f8fafc; border-left:4px solid #e53935; border-radius:4px 8px 8px 4px; padding:12px 16px; font-size:14px; line-height:1.6; color:#1e293b; box-shadow:0 1px 2px rgba(0,0,0,0.04);'>
      <b>Nature of Secondary Analysis:</b> As a secondary analysis of a cluster randomized trial, the study is constrained by the original trial's design and data collection protocols, limiting the ability to adapt sampling strategies for new research questions.
    </div>
    
    <div style='background:#f8fafc; border-left:4px solid #e5a823; border-radius:4px 8px 8px 4px; padding:12px 16px; font-size:14px; line-height:1.6; color:#1e293b; box-shadow:0 1px 2px rgba(0,0,0,0.04);'>
      <b>Statistical Power Constraints:</b> Due to the sharp decline in DENV-3 cases after August, the analytical scope was expanded to include all general Aedes-borne viruses (ABV). This aggregation may obscure the unique transmission dynamics of individual virus strains.
    </div>

    <div style='background:#f8fafc; border-left:4px solid #2f69b1; border-radius:4px 8px 8px 4px; padding:12px 16px; font-size:14px; line-height:1.6; color:#1e293b; box-shadow:0 1px 2px rgba(0,0,0,0.04);'>
      <b>Temporal Generalizability:</b> The analysis specifically focuses on the 2023 season, which was an anomalous year characterized by an unprecedented high volume of cases. The spatial clustering patterns observed during this extreme outbreak may not be fully applicable to standard or low-transmission seasons.
    </div>

    <div style='background:#f8fafc; border-left:4px solid #1f3b73; border-radius:4px 8px 8px 4px; padding:12px 16px; font-size:14px; line-height:1.6; color:#1e293b; box-shadow:0 1px 2px rgba(0,0,0,0.04);'>
      <b>Intervention Threshold:</b> The effectiveness of targeted indoor residual spraying (TIRS) is highly sensitive to the timing of deployment. Once viral transmission transitions from localized clusters to a citywide disseminated phase, community-level interventions alone are no longer sufficient.
    </div>

  </div>
</div>
")
```

